Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-14 presentations/bsa_2020-07-27/index.Rmd
update slides

## (Very brief) introduction to the biogeography of Japan

- Wide variation in climate from north (subarctic) to south (subtropical)

@@

- Main islands continental, southern islands oceanic

>>>>

---
background-position: 40% 50%
background-image: url(images/japan_intro.png)
background-size: contain

## A (very brief) introduction to the biogeography of Japan

.pull-left[
- Wide variation in climate from north (subarctic) to south (subtropical)

@@

- Main islands continental, southern islands oceanic
]
